% LaTeX resume using res.cls
\documentclass[12pt,line,letterpaper]{res}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\setlength{\topmargin}{-0.3in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header

\begin{document}

\name{\LARGE{Aaron J. Peschel}}
% \address used twice to have two lines of address
\address{968 Washington St Apt 4, San Francisco, CA}
\address{aaron.peschel@gmail.com or (760)-791-7301}

\begin{resume}
\pagestyle{empty}
\section{Experience}
    {\bf Systems Engineer} \hfill September 2016 - Current \\
    Element Analytics, San Francisco, CA
    \begin{itemize} \itemsep -2pt
    \item Prototyped Kubernetes and transitioned the application stack to run on Kubernetes.
    \item Reworked Azure ARM deployment process to reduce application deploy time from over a day to a couple of hours.
    \item Worked with vendors to find appropriate solutions for logging, metrics, and other platform services.
    \item Encapsulated the application services in Helm charts for deployment.
    \item Provided training and guidance for the development teams on the best practices for Docker, Kubernetes, and build pipelines.
    \item Planning for quarter long projects, breaking them into smaller, sprint-sized stories.
    \end{itemize}

    {\bf Development Operations Engineer} \hfill April 2012 - June 2016 \\
    Zendesk, San Francisco, CA
    \begin{itemize} \itemsep -2pt
    \item Coordinated with security team to achieve PCI compliance in production environment.
    \item Set up an LDAP infrastructure for production environment. Migrated all users, groups, and SUDOers rules.
    \item Orchestrated deployment of new developer projects to production environment. This included planning the architecture for the project, planning basic networking, writing Chef cookbooks, and planning the overall project timeline.
    \item Created a secure isolated environment for the professional services team using AWS, OpenVPN, and Openswan.
    \item Worked with open source projects to merge bug fixes and features into the main code base, rather than running in-house forks.
    \item Was responsible for 24/7 on-call shift coverage of production environment.
    \end{itemize}

    {\bf Associate Systems Engineer} \hfill September 2010 - April 2012 \\
    Autonomy, Pleasanton, CA
    \begin{itemize} \itemsep -2pt
    \item Headed US support of Optimost network which involved maintaining existing environments and deploying new environments.
    \item Wrote puppet manifests to manage the deployment and configuration of servers.
    \item Researched and deployed tools like Cobbler, Koan, Xen, and Virsh to improve the efficiency of the Optimost environment.
    \item Performed troubleshooting on intricate domain-specific problems within a distributed system.
    \item Performed limited network administration duties such as firewall, load balancer, and routing configuration.
    \end{itemize}

\section {Open Source Project Contributions}
    {\bf NGINX:} added weak ETag support \\
    {\bf Cobbler:} various bug fixes \\
    {\bf Siege:} added SNI support \\
    {\bf Docker Compose API:} added support for V2 docker-compose configs

\section{Strongest Tools / Skills / Relevant Buzzword List}
    {\bf Languages:} Python, Ruby, Bash, C \\
    {\bf Orchestration:} Puppet, Chef, Kubernetes \\
    {\bf Administration:} Nagios, Datadog, systemd, Pagerduty, Git \\
    {\bf Networking:} OpenLDAP, NGINX, IPTables, HAProxy, Keepalive \\
    {\bf Virtualization:} Xen, AWS, Docker, LXC

\section{Education}
    {\bf B.S., Computer Science and Engineering} \hfill December 2009 \\
    Parallel and Distributed Computing Track \\
    {\bf Minor in Management} \\
    University of California, Irvine, GPA: 3.655, \textit{cum laude}

\end{resume}
\end{document}
