% LaTeX resume using res.cls
\documentclass[10pt,line,margin]{res}
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{Aaron J. Peschel}
% \address used twice to have two lines of address
\address{4245 Stanley Blvd Pleasanton, CA}
\address{jobs@apeschel.fastmail.fm or (760)-791-7301}

\begin{resume}
\vfill
\section{OBJECTIVE}
    Seeking a full time entry-level developement position that will utilize my
    training and background in Computer Science, Mathematics, and
    Engineering - as well as my versatility and commitment to excellence.

\section{EDUCATION}
    {\bf B.S., Computer Science and Engineering} \hfill December 2009 \\
    Parallel and Distributed Computing Track \\
    {\bf Minor in Management} \\
    University of California, Irvine, GPA: 3.655, \textit{cum laude}

\section{EXPERIENCE}
    {\bf Associate Systems Engineer} \hfill September 2010 - Current \\
    Autonomy, Pleasanton, CA
    \begin{itemize} \itemsep -2pt
    \item Maintains a large scale Linux network.
    \item Uses deductive skills to fix problems with servers.
    \item Creates simple Python scripts to automate tasks.
    \end{itemize}

    {\bf Math Tutor} \hfill November 2005 - June 2006 \\
    Imperial Valley College, Imperial, CA
    \begin{itemize} \itemsep -2pt
    \item Tutored students in math related topics from
    algebra to multi variable calculus.
    \end{itemize}

    {\bf Vice President of Student Government}
    \hfill  October 2005 - June 2006 \\
    Imperial Valley College, Imperial, CA
    \begin{itemize} \itemsep -2pt
    \item   Acted as the voice of students at school board meetings.
    \item Managed school events with other student government
    members.
    \end{itemize}

\section {PROJECTS}
    {\bf Optical Networking Senior Design Project} \hfill Fall 2008 to Spring 2009
    \begin{itemize} \itemsep -2pt
    \item Year long team project to create a simple wireless
    networking device from basic circuit elements.
    \item Programmed an embedded microprocessor in C.
    \item Overcame several major setbacks to complete the project.
    \end{itemize}

    {\bf UNIX Shell} \hfill Spring 2008
    \begin{itemize} \itemsep -2pt
    \item Developed a fully operational UNIX shell in C, which
    supports features such as multiple pipes, background processes,
    and input/output redirection.
    \item Created a basic version of the ls command in C.
    \end{itemize}

    {\bf Basic OpenGL Implementation} \hfill Winter 2008
    \begin{itemize} \itemsep -2pt
    \item Used C++ to implement portions of the OpenGL library
    related to lighting, transforms, and perspective.
    \end{itemize}

\section{TECHNICAL \\ SKILLS}
    {\bf Languages:} Proficient with Python, C, C++, and Java \\
    {\bf Development:} IDEs (Eclipse, Visual Studio), GNU
    Toolchain (GCC, GDB), \\ SCM Tools (RCS, CVS, SVN) \\
    {\bf Operating Systems:} UNIX, Linux, Windows Vista/XP \\
    {\bf MISC:} Text editors (Vim, Textpad), Moderate Understanding 
    of Databases

\section {RELEVANT \\ COURSEWORK}
    Statistics and Probability for Engineers,
    Distributed Systems, Parallel Computer Systems, Digital
    Signal Processing Embedded Computing Systems, Programming
    in Multitasking Operating Systems, Project in Operating
    System Organization,

\end{resume}
\end{document}
